---
#output: github_document
output: html_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SpaceX

<!-- badges: start -->
<!-- badges: end -->

The goal of SpaceX is to provide shared and cluster specfic gene co-expression networks for spatial transcriptomics data.

## Installation

This package requires a Fortran compiler in order to work.  Here are the instructions:

+ Windows:  install the Rtools package that is appropriate for your version of R

+ Mac:  Go to this website and follow the instructions:  (https://mac.R-project.org/tools/)

+ Linux:  From a terminal, do the following: `sudo apt install gcc`.  That will bring in multiple compilers.



The package requires a dependency that is not available on CRAN. Install it with:

``` r
remotes::install_github("rdevito/MSFA")
```

You can install the released version of SpaceX from (https://github.com/SatwikAch/SpaceX) with:

``` r
devtools::install_github("SatwikAch/SpaceX")
```


```{r}
library(SpaceX)
```

```{r , eval=FALSE} 
## Reading the Breast cancer data

## Spatial locations
head(BC_loc)

## Gene expression for data
head(BC_count) 

## Data processing
G <-dim(BC_count)[2] ## number of genes
N <-dim(BC_count)[1] ## number of locations

## Application to SpaceX algorithm
BC_fit <- SpaceX(BC_count,BC_loc[,1:2],BC_loc[,3],sPMM=FALSE,Post_process = TRUE)

## Shared_network :: Shared co-expression matrix
## Cluster_network :: Cluster specific co-expression matrices

```

You can view the supplementary file at this link: https://bookdown.org/satwik91/SpaceX_supplementary/.
